CGAT In The Hat

### 2012-12-06 paper/paper.tex
Working on implementation section in paper.

\section{Implementation}\label{sec:implementation}
CGAT uses a standard LAMP stack with MySQL traded out for MongoDB.

@@

Mongo's PHP connecter is fully featured.
TODO(eriq): Cite mongo's php connector.

\subsubsection{Database Schema}

\subsubsection{API}
CGAT is an entireley API driven product. The API is central to all the behavior.
The API supplies \textbf{all} the information that is displayed in the UI.
This is a very important design choice. Having the API be the sole data provider and manipulator for the system
means that all functionality can be programatically provided and different applications can present the same
fuinctionality with a different UI.

@@

\paragraph{GET Requests}
\begin{itemize}
\item administration_info - Provides the user with meta information information that the user would need to perform administrative tasks such as greating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign_task - Ask a group of people to perform an annotation.
\item cancel_notification - Clear a notification from a user.
\item create_annotation - Create a new annotation of a contig.
\item create_group - Create a group.
\item join_group - Join a group.
\item leave_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save_annotation - Save a work-in-progress annotation.
\item set_help - Upload a help page.
\item submit_annotation - Submit a finalized annotaion.
\item upload_contig - Uplaod a contig into CGAT.
\end{itemize}

\subsection{Frontend}

\section{UI Design}\label{sec:ui}

>>>>

\section{Implementation}\label{sec:implementation}
CGAT uses a standard LAMP (Linux Apache MySQL PHP) stack with MySQL traded out for MongoDB.

@@

PHP and MongoDB work together very nicely and MongoDB's PHP connector is fully featured \cite{phpMongo}.

\subsubsection{Database Schema}
Although we use MongoDB which does not enforce a specific schema, by convention we enforce a schema on our documents.
MongoDB uses BSON (Binary JSON). BSON is an extended JSON format that supports additional types like a datetimes \cite{bson}.

The schemas for our four JSON objects are shown in Figures \ref{fig:JSON-contig}, \ref{fig:JSON-annotation},
\ref{fig:JSON-user}, and \ref{fig:JSON-group} in Appendix \ref{sec:data_models}.

\subsubsection{API}
CGAT is an entirely API driven product. The API is central to all the behavior.
The API supplies \textbf{all} the information that is displayed in the UI.
This is a very important design choice. Having the API be the sole data provider and manipulator for the system
means that all functionality can be programmatically provided and different applications can present the same
functionality with a different UI.

@@

\paragraph{GET Requests}
\begin{itemize}
\item administration_info - Provides the user with meta information information that the user would need to perform administrative tasks such as creating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign_task - Ask a group of people to perform an annotation.
\item cancel_notification - Clear a notification from a user.
\item create_annotation - Create a new annotation of a contig.
\item create_group - Create a group.
\item join_group - Join a group.
\item leave_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save_annotation - Save a work-in-progress annotation.
\item set_help - Upload a help page.
\item submit_annotation - Submit a finalized annotation.
\item upload_contig - Upload a contig into CGAT.
\end{itemize}

\subsection{Frontend}
CGAT's frontend uses standard web technologies (HTML, Javascript, and CSS).
CGAT uses many HTML5/CSS3 features such as transforms and pseudo-elements.

Because the entire system is API based, the frontend heavily relies on asynchronous fetches (AJAX).
